---
title: "A Brief R Markdown Tour"
author: "Matteo Rizzuto"
date: "January 26, 2021"
output: 
  ioslides_presentation:
    widescreen: true
    logo: lablogo.png
---

# Roadmap

- Philosophy
- What is R Markdown?
- Why R Markdown?
- Basics of R Markdown
    + Installation
    + Plain text and Code Chunks
    + Figures
    + Tables
    + Output
- Advanced Stuff
    + References and Bibliographies
    + Interactive Figures
    + Look and Feel
- Bonus (if we have time)
    + Version Control with git

# Introduction

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

